\documentclass[fleqn, a4paper, 11pt, oneside]{amsart}
\usepackage{exsheets}
\usepackage{amsmath, amssymb, amsthm} %standard AMS packages
\usepackage{marginnote} %marginnotes
\usepackage{gensymb} %miscellaneous symbols
\usepackage{commath} %differential symbols
\usepackage{xcolor} %colours
\usepackage{cancel} %cancelling terms
\usepackage[free-standing-units, space-before-unit]{siunitx} %formatting units
\usepackage{tikz, pgfplots} %diagrams
	\usetikzlibrary{calc, hobby, patterns, intersections, decorations.markings}
\usepackage{graphicx} %inserting graphics
\usepackage{hyperref} %hyperlinks
\usepackage{datetime} %date and time
\usepackage{enumerate,enumitem} %numbered lists
\usepackage{float} %inserting floats
\usepackage{circuitikz}[american voltages, american currents] %circuit diagrams
\usepackage{algpseudocode} %algorithms
\usepackage{algorithm} %algorithms
\usepackage{booktabs}
\usepackage{xspace}

\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}} %adds numbers to specific equations in non-numbered list of equations

\theoremstyle{definition}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}

\theoremstyle{theorem}
\newtheorem{theorem}{Theorem}

\makeatletter
\@addtoreset{section}{part} %resets section numbers in new part
\makeatother

\DeclareMathOperator{\comp}{\textsc{c}}

\DeclareMathOperator{\prob}{\mathrm{P}}

\DeclareMathOperator{\expct}{\mathrm{E}}

\DeclareMathOperator{\var}{\mathrm{V}}

\DeclareMathOperator{\bin}{\mathrm{Bin}}

\DeclareMathOperator{\poi}{\mathrm{Poi}}

\DeclareMathOperator{\geo}{\mathrm{Geo}}

\DeclareMathOperator{\nb}{\mathrm{NB}}

\DeclareMathOperator{\hg}{\mathrm{HG}}

\newcommand*{\perm}[2]{{}^{#1}\mathrm{P}_{#2}}%
\newcommand*{\comb}[2]{{}^{#1}\mathrm{C}_{#2}}%

\newcommand{\A}{\text{Alice}\xspace}
\newcommand{\B}{\text{Bob}\xspace}
\newcommand{\C}{\text{Charlie}\xspace}
\newcommand{\D}{\text{David}\xspace}
\newcommand{\E}{\text{Eve}\xspace}
\newcommand{\F}{\text{Frank}\xspace}

\SetupExSheets{solution/print = true}

%opening
\title
[
	Introduction to Probability and Statistics : Assignment 5
]
{
	Introduction to Probability and Statistics\\
	Assignment 5
}
\author
{
	Aakash Jog\\
	ID : 989323563
}
\date{\formatdate{13}{3}{2016}}

\begin{document}

\maketitle
%\setlength{\mathindent}{0pt}

\begin{question}
	If $X$ is a binomial random variable with expected value $6$ and variance $2.4$, find $\prob(X = 5)$.
\end{question}

\begin{solution}
	\begin{align*}
		\expct[X] &= 6\\
		\therefore n p &= 6\\
		\var(X) &= 2.4\\
		\therefore n p (1 - p) &= 2.4
	\end{align*}
	Therefore,
	\begin{align*}
		1 - p &= 0.4\\
		\therefore p &= 0.6
	\end{align*}
	Therefore,
	\begin{align*}
		\prob(X = i) &= \comb{n}{i} (p)^i (1 - p)^{n - i}\\
		\therefore (X = 5) &= \comb{10}{5} (0.6)^5 (0.4)^5
	\end{align*}
\end{solution}

\begin{question}
	Each member of a seven judge panel independently makes a correct decision with probability $0.7$.
	If the panel's decision is made by majority rule, what is the probability that the panel makes the correct decision?
	Given that four of the judges agreed, what is the probability that the panel made the correct decision?
\end{question}

\begin{solution}
	Let $A$ be the decision that the panel makes the correct decision.\\
	Let $B$ be the decision that four of the judges agree.\\
	Therefore,
	\begin{align*}
		\prob(A) &= \sum\limits_{i = 4}^{7} \comb{7}{i} (0.7)^i (0.3)^{7 - i}
	\end{align*}
	Therefore,
	\begin{align*}
		\prob(A|B) &= \frac{\prob(A \cap B)}{\prob(B)}\\
		&= \frac{\comb{7}{4} (0.7)^4 (0.3)^3}{\comb{7}{4} (0.7)^4 (0.3)^3 + \comb{7}{4} (0.3)^4 (0.7)^3}
	\end{align*}
\end{solution}

\begin{question}
	A player bets on a number from $1$ to $6$.
	Three dice are then rolled, and if the number bet by the player appears $i$ times, where $i = 1,2,3$, then the player wins $i$ units.
	If the number bet by the player does not appear on any of the dice, then the player loses $1$ unit.
	Is this game fair to the player?
\end{question}

\begin{solution}
	Let $X$ be the player's winnings.\\
	Let $Y$ be the number of times the number the player bet on appeared.
	Therefore,
	\begin{align*}
		Y & \sim \bin\left( 3,\frac{1}{6} \right)
	\end{align*}
	Therefore,
	\begin{align*}
		\prob(X = -1) & = \prob(Y = 0)                                                          \\
                              & = \comb{3}{0} \left( \frac{1}{6} \right)^0 \left( \frac{5}{6} \right)^3 \\
                              & = \frac{125}{216}                                                       \\
		\prob(X = 1)  & = \prob(Y = 1)                                                          \\
                              & = \comb{3}{1} \left( \frac{1}{6} \right)^1 \left( \frac{5}{6} \right)^2 \\
                              & = \frac{75}{216}                                                        \\
		\prob(X = 2)  & = \prob(Y = 2)                                                          \\
                              & = \comb{3}{2} \left( \frac{1}{6} \right)^2 \left( \frac{5}{6} \right)^1 \\
                              & = \frac{15}{216}                                                        \\
		\prob(X = 3)  & = \prob(Y = 3)                                                          \\
                              & = \comb{3}{3} \left( \frac{1}{6} \right)^3 \left( \frac{5}{6} \right)^0 \\
                              & = \frac{1}{216}
	\end{align*}
	Therefore,
	\begin{align*}
		\expct[X] & = (-1) \left( \frac{125}{216} \right) + (1) \left( \frac{75}{216} \right) + (2) \left( \frac{15}{216} \right) + (3) \left( \frac{1}{216} \right) \\
                          & = -\frac{17}{216}
	\end{align*}
	Therefore, as the expected value of the winnings is less than $0$, the game is not fair towards the player.
\end{solution}

\begin{question}
	Surveys indicated that $40\%$ of the Zulu tribe members use the toothpaste `Zebra'.
	A marketing company wants to interview a user of that toothpaste.
	Let $X$ be the number of persons that the company would contact until a person who uses `Zebra' will be found.
	\begin{enumerate}
		\item
			What is the distribution of $X$?
		\item
			What is the expectation and variance of $X$?
		\item
			What is the probability that the company will interview at most $3$ persons until a `Zebra' user is found?
		\item
			Let $Y$ be the number of clients that the company would contact until $2$ persons who `Zebra' will be found.
			What is the distribution of $Y$?
		\item
			What is the expectation and variance of $Y$?
	\end{enumerate}
\end{question}

\begin{solution}
	\begin{enumerate}[leftmargin=*]
		\item
			$X$ is a geometric random variable, with probability $0.4$ for success.
			Therefore,
			\begin{align*}
				X &\sim \geo(0.4)
			\end{align*}
		\item
			\begin{align*}
				X &\sim \geo(0.4)
			\end{align*}
			Therefore,
			\begin{align*}
				\expct[X] &= \frac{1}{p}\\
				&= \frac{1}{0.4}\\
				&= 2.5\\
				\var(X) &= \frac{1 - p}{p^2}\\
				&= \frac{1 - 0.4}{(0.4)^2}\\
				&= \frac{0.6}{0.16}\\
				&= 3.75
			\end{align*}
		\item
			\begin{align*}
				X &\sim \geo(0.4)
			\end{align*}
			Therefore,
			\begin{align*}
				\prob(X \le 3) &= 1 - \prob(X > 3)\\
				&= 1 - \sum\limits_{k = 4}^{\infty} (1 - p)^{k - 1} p\\
				&= 1 - (1 - p)^3\\
				&= 1 - (0.6)^3\\
				&= 1 - 0.216\\
				&= 0.784
			\end{align*}
		\item
			\begin{align*}
				X &\sim \nb(2,0.4)
			\end{align*}
		\item
			\begin{align*}
				X &\sim \nb(2,0.4)
			\end{align*}
			Therefore,
			\begin{align*}
				\expct[X] &= \frac{r}{p}\\
				&= \frac{2}{0.4}\\
				&= 5\\
				\var(X) &= \frac{r (1 - p)}{p^2}\\
				&= \frac{(2) (0.6)}{(0.4)^2}\\
				&= \frac{0.12}{0.16}\\
				&= 7.5
			\end{align*}
	\end{enumerate}
\end{solution}

\begin{question}
	In the Israeli Parliament, the Knesset, $24$ out of $120$ MPs are women.
	\begin{enumerate}
		\item
			If you randomly choose chairpersons for the $12$ parliamentary committees, what are the chances that exactly $3$ of them are women, given that
			\begin{enumerate}
				\item Each MP can be a chairperson of any number of committees.
				\item Each MP can be a chairperson of at most one committee.
			\end{enumerate}
		\item
			Which method is better for promoting gender equality?
	\end{enumerate}
\end{question}

\begin{solution}
	\begin{enumerate}[leftmargin=*]
		\item
			Let $X$ be the number of parliamentary committees which have women as chairpersons such that a MP can chair any number of committees.
			Therefore,
			\begin{align*}
				X &\sim \bin\left( 12,\frac{24}{120} \right)\\
				&\sim \bin\left( 12,\frac{1}{5} \right)
			\end{align*}
			Therefore,
			\begin{align*}
				\prob(X = 3) &= \comb{12}{3} \left( \frac{1}{5} \right)^3 \left( \frac{4}{5} \right)^9\\
				&= 0.2362232013
			\end{align*}
		\item
			Let $X$ be the number of parliamentary committees which have women as chairpersons such that a MP can chair at most one committee.
			Therefore,
			\begin{align*}
				X &\sim \hg\left( 12,120,24 \right)
			\end{align*}
			Therefore,
			\begin{align*}
				\prob(X = 3) &= \frac{\comb{12}{3} \comb{120 - 24}{12 - 3}}{\comb{120}{12}}\\
				&= \frac{\comb{12}{3} \comb{96}{9}}{\comb{120}{12}}\\
				&= 0.02705523278
			\end{align*}
	\end{enumerate}
\end{solution}

\begin{question}
	\A likes hippopotamuses and walks daily with \B to the zoo.
	The walking time to the zoo is distributed uniformly between $15$ and $20$ minutes with intervals of $1$ minute.
	\begin{enumerate}
		\item What is the chance that on a random day, \A and \B would not walk more than $17$ minutes?
		\item What is the expectation and variance of the walking time to the zoo?
		\item What is the probability that today and tomorrow the walking time would exceed $19$ minutes?
	\end{enumerate}
\end{question}

\end{document}
